```{r}
#connecting to a database that we have currently stored in our data folder

library(DBI)

filename<- "../data/prod_sample.db"
my_connection<- dbConnect(RSQLite::SQLite(),
                          dbname = filename)
my_connection
```

```{r}
#Check what tables exist in this database
dbListTables(my_connection)
```

```{sql connection =my_connection}
/* sql query to view the first ten rows of the online_retail_history table */
select *
  from online_retail_history
limit 10
```
``````{sql connection =my_connection}
/* sql query to view the first ten rows of the online_retail_history table */
select *
  from stock_description
limit 5

```
```{sql connection=my_connection}
/* SQLFUNCTIONS - COUNT()-SUM()-AVG()-MIN()-MAX() */
select count(*) as number_rows
from online_retail_history


```
```{sql connection=my_connection}
/* calculate the total number */
select sum(quantity) as total_quantity
from online_retail_history
```
```{sql connection=my_connection}
/*average price of product */
select avg(price) as avg_price
from online_retail_history
```
```{sql connection=my_connection}
/* min price of product sold */
select min(price) as min_price
from online_retail_history
where price>0
```
```{sql connection=my_connection}
/* calculate the max price */
select max(price) as max_price
from online_retail_history

```
```{sql connection=my_connection}
/* 1. calculate the number of unique customers */
select count(distinct CustomerID) as munber_unique_customers
from online_retail_history
```
```{sql connection=my_connection}
/* 2 count invoces*/
select count(distinct Invoice) as number_of_invoice
from online_retail_history
```
```{sql connection=my_connection}
/* 3. when was the first and last invoice */
select min(InvoiceDate) as first_invoice,
max(InvoiceDate) as last_invoice
from online_retail_history
```
```{sql connection=my_connection}
/* 4. how many diff types of stocks did the customers purchase? */
select count(distinct StockCode) as number_stock_types
from online_retail_history
```
```{sql connection=my_connection}
/* 5. how many stocks does the stock_table contain? */
select count(distinct StockCode) as number_stocks
from stock_description
```
```{r}
dbDisconnect(my_connection)
```

