
```
title: "Visualising Data"
```

```{r}
#read the csv file and save as a variable called heart_data
setwd("/Users/vandavinecka/Desktop/Uni/intro-to-programming/notebooks")

heart_data<- read.csv("../data/heart_attack_data.csv")
```

#head function to preview the data
```{r}
head(heart_data)
```

#check the shape of the data (number of rows and columns)
```{r}
dim(heart_data)
```
```{r}
#check the structure  of the data (different  data type of the DataFrame)
str(heart_data)
```

#Categorise the following variables
```{r}
heart_data$sex <-factor(heart_data$sex)
heart_data$cp <-factor(heart_data$cp)
heart_data$fbs <-factor(heart_data$fbs)
heart_data$restecg <-factor(heart_data$restecg)
heart_data$exang <-factor(heart_data$exang)
heart_data$target <-factor(heart_data$target)
summary(heart_data)
```
```{r}
str(heart_data)
```
```{r}
#install.packages ("tidyverse") - 7 packages of Rcode
library(tidyverse )
```
#visualising data in R - THE SYNTEX
#name_of_data_frame%>%
#ggplot(mapping = aes([MAPPING])) + [GEOM_FUNCTION] ()
#To create  a line graph  with ggplot() + geom_line()function.
#To create  a scatter  plot, we use ggplot() + geom_point()
#To create  a histogram,  we use ggplot() + geom_histogram()
#To create  a bar chart  we use ggplot() + geom_bar()
#To create  a boxplot,  we use ggplot() + geom_boxplot()

```{r}
#start with defining the x and y axis
#look at the relationship between age and chol

heart_data%>%
  ggplot(aes(x=age, y=chol))
  
```
```{r}
heart_data%>%
  ggplot(aes(x=age, y=chol)) + 
  geom_point(na.rm = TRUE)
```
```{r}
#aes -Aesthetic mapping
heart_data%>%
  ggplot(aes(x=age, y=chol)) + 
  geom_point(aes(color =sex),na.rm = TRUE)+
# add title for the scatter plot
ggtitle("Age vs.Chol by Gender")
```
```{r}
#optional: if you want to replace 0 and 1 with "female and male"

heart_data<- heart_data%>%
  mutate(sex = ifelse(sex == 0, "Female","Male"))

unique(heart_data$sex)
```

```{r}
heart_data%>%
  ggplot(aes(x=age, y=chol)) + 
  geom_point(aes(color =sex),na.rm = TRUE)+
# add title for the scatter plot
ggtitle("Age vs.Chol by Gender")
```
```{r}
#Visualize the relationship between age,chol and heart disease(target)
heart_data%>%
  ggplot(aes(x = age,y = chol)) +
  geom_point(aes(color = target),na.rm = TRUE) +
  ggtitle("Relationship between age,chol and heart disease")
```

```{r}
heart_data<- heart_data%>%
  mutate(target = ifelse(target == 0, "No heart disease","heart disease"))

unique(heart_data$target)
```
```{r}
heart_data%>%
  ggplot(aes(x = age,y = chol)) +
  geom_point(aes(color = target),na.rm = TRUE) +
  ggtitle("Relationship between age,chol and heart disease")
```
```{r}
#adjust the color of the histogram
heart_data%>%
  ggplot(aes(x=age)) +
  geom_histogram(birwidth=5, fill= "blue", color="pink",aplha=0.9) +
  ggtitle("Histogram with bin size = 5") +
  theme(plot.title = element_text(size=15))
```

